DisCon Children 6 exposure trials

### 2019-07-31 analysis/02_kids_600.Rmd
speaker change experiment for kids

```{r}
chance_data <- data %>%
  filter(phase != "training") %>%
  group_by(subage,subid) %>%
  summarise(correct = mean(correct_target1)) %>%
  mutate(comp_chance= ifelse(correct<1/3,0,1))

@@

chance_model <- brm(comp_chance ~ 1,
                    data = chance_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

>>>>

```{r}
model_data <- data%>%
  filter(phase != "training")%>%
  mutate(age_num = scale(age_num))

@@

chance_model <- brm(correct_target1 ~ 1 + 
                      (1| subid) + (age_num | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)
